---
title: "Let's see what MUTE and SPEECHLESS bait, CATCHES"
author: "Ann Loraine and Diego Lopez"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The Introduction states, explains, and justifies the question motivating the study. 

State: 

* The question you are trying to answer

Explain:

* Why the question is important.
* How you intend to answer the question, e.g., the approach you're using. 
* Provide links to external datasets you're using.

Here is an example "Introduction" section:

The central limit theorem in statistics is one of the most important 
mathematical results in history! 

One aspect of the central limit theorem is that if you sample a population over and over again, and compute the averages for each sample, then these averages will be normally distributed, with sample average fluctuating around the population average. 

In this Markdown, we ask the question:

* Using R's random number generation features, can we observe the normal distribution of sample averages? 

## Results and Analysis

This section analyzes data and states results from the analysis, focusing on
answering the question(s) stated in the Introduction.

What is a result? A "result" is fact that your code demonstrates is true. 
That is all it is. Nothing more. The actual meaning you ascribe to the fact - its
importance or significance - is an "interpretation" of the fact. 

The Results section should contain sets of code chunks and their results. 

You'll probably include many code chunks. Each chunk and the output it produces
produces a result and also demonstrates that the result is correct.

Following each chunk, state the fact that the code demonstrates.

A figure is a visual representation of many results.
After each figure, you should state one or more results
demonstrated in the figure. 

Also, provide a legend or other statement defining
axes and units in the figure. 

Here is an example of a part of a Results and Analysis section:

* * *

In the following code chunk, we create an example data set using a function in R that generates random samples from the exponential distribution, using the default value of 1 for the rate parameter.

First, make the random number generation reproducible:

```{r}
set.seed(7)
```

Create random samples from the exponential distribution:

```{r}
sample_size = 50
num_samples = 100
exponential_random_samples = replicate(num_samples,
                                       rexp(sample_size,rate=1))
```

The matrix `exponental_random_samples` has `r ncol(exponential_random_samples)` columns, where each column represents a random sampling`from the exponential distribution. 

Each sample contains `r nrow(exponential_random_samples)` values. 

To illustrate that the samples are from the exponential distribution, show a histogram of values from the first random sample:

```{r fig.height=4, fig.width=4}
main="Sample 1"
hist(exponential_random_samples[,1],main=main,probability = T)
```

The preceding figures show that the random samples contain values selected at random from the exponential distribution. 

Compute the average of each random sample, saving the result to a vector:

```{r}
averages = apply(exponential_random_samples,2,mean)
```

Display a histogram showing the distribution of sample averages from the random samples:

```{r fig.height=4, fig.width=4}
main="Sample average histogram"
xlab = "Sample averages"
hist(averages,main=main,xlab=xlab,probability = T)
```

The figure shows that the sample averages follow a normal distribution, centered on the rate parameter of 1.

* * *

## Discussion

In this section, write about the facts presented in the Results section.

* Restate the question from the Introduction. 
* Explain how the facts presented in the Results section answer the question.
* Describe possible limitations of the study.
* Describe how answering the question creates new knowledge; put the Results into the larger context of what is already known.

* * *

Here is an example:

In the Introduction section, we introduced the main question motivating this study, which was: Can we use R functions to confirm that sample averages are normally distributed, even when the sample values themselves are not? 

To show this, we made a matrix of randomly selected values from the exponential distribution with rate parameter set to 1. 

The columns of the matrix represented the samples, and the rows represented observations per sample. There were `r num_samples` samples
of `r sample_size` values per sample.

The first figure, a histogram, showed how the first random sample was from the exponential distribution, as it had a characteristic non-symmetrical shape. We did not examine all the samples, as there were too many.

The second figure, also a histogram, showed that the averages of all these samples followed a normal distribution, as expected. These values centered on 1, the rate parameter.

* * *

## Conclusion

This section states the answer to the question. 

* Use bullet points to state the major findings from the study.
* Provide the "too long didn't read" summary for people who don't want to bother with reading anything else.

* * *

Here is an example Conclusion section:

* R can be used to show that sample averages are normally distributed.

* * *